Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-12 providence/sections/intro.tex
some more stuff on rlas

%Intro
It is well-known that electronic voting systems are vulnerable to software errors and manipulation which may be undetected. Errors and/or manipulation may not always change an election outcome, but we would want to know when they do. {\em Software independent} voting systems \cite{SI-Wack,rivest2008notion} are ones where an undetected change in the software cannot lead to an undetectable change in the election outcome. {\em Evidence-based elections} \cite{evidence-based} use software independent systems to produce trustworthy evidence of outcome correctness; incorrect outcomes are detected with high probability when the evidence is examined. One approach to evidence-based elections is to use voter-verified paper ballots, store them securely, and perform public audits---a compliance audit to determine whether the ballots were stored securely; and a rigorous tabulation audit, known as a risk-limiting audit (RLA) \cite{RLA}, to determine whether the outcome is correctly computed from the stored ballots.  A {\em risk-limiting audit} guarantees a minimum probability of a full hand count if the election outcome is incorrect. Conversely, it guarantees a maximum probability of audit error, termed the {\em risk limit}, which is the maximum probability with which the audit would declare an incorrect election outcome as being correct.

>>>>

%Intro
It is well-known that electronic voting systems are vulnerable to software errors and manipulation which may be undetected. Errors and/or manipulation may not always change an election outcome, but we would want to know when they do. {\em Software independent} voting systems \cite{SI-Wack,rivest2008notion} are ones where an undetected change in the software cannot lead to an undetectable change in the election outcome. {\em Evidence-based elections} \cite{evidence-based} use software independent systems to produce trustworthy evidence of outcome correctness; the evidence is examined so that incorrect outcomes may be detected with high probability. One approach to evidence-based elections is to use voter-verified paper ballots, store them securely, and perform public audits---a compliance audit to determine whether the ballots were stored securely; and a rigorous tabulation audit, known as a risk-limiting audit (RLA) \cite{RLA}, to determine whether the outcome is correctly computed from the stored ballots.

An audit will either end with a declaration that an election outcome is correct, or escalate to a full hand count. It may be evaluated based on how it deals with incorrect election outcomes, as the purpose is to detect these. A {\em risk-limiting audit (RLA)} guarantees a minimum probability of a full hand count if the election outcome is incorrect; this is the probability of correct functioning of the audit. Equivalently, an RLA guarantees a maximum probability of audit error if the election outcome is incorrect. This error measure is termed the {\em risk limit}, more rigorously defined as the maximum probability with which the audit would declare an incorrect election outcome as being correct.
